---
title: 'S2_MGF Figure 4: Differential Rankings'
author: "Stephen Formel"
date: "12/4/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, out.width = "100%")
```

### S2_MGF Manuscript  Figure 4 - Ranked Differential plots

Last updated 4 Dec 2020 by Steve Formel

Description: I'm basically imitating the QURRO plots: https://www.biorxiv.org/content/10.1101/2019.12.17.880047v1.full

### Load libraries

```{r message = FALSE}

library(tidyverse)
library(ggforce)
library(cowplot)
library(ggrepel)
library(grid)
library(venn)
library(ggplot2)
library(ggpolypath)

```

### Load and Clean data

```{r, message = FALSE}

source("./S2_MGF_load_packages_and_clean_data.R")

# Load Songbird output

sb <- read.delim("../../../../songbird/logdir/new_final_3/fungi/S2_MG_fungi_site_season/differentials.tsv")

#rename columns
names(sb) <- c("featureid", "Intercept", "Fourchon_rel_BJ", "Summer_rel_Wint")

#Using not filtered because the biom used in songbird wasn't filtered this way 
fung.2season.sub <- subset_taxa(fung.2season_with_outliers, rownames(tax_table(fung.2season_with_outliers)) %in% sb$featureid)
 
sb.filtered <- sb[sb$featureid %in% rownames(tax_table(fung.2season_with_outliers_filtered)), ]

#bind taxonomy with songbird results
sb <- cbind(sb, tax_table(fung.2season.sub))

#Factor for whether something is dominant or not

sb$rare_dom <- factor(ifelse(sb$featureid %in% sb.filtered$featureid,
                      "dominant",
                      "rare"))

#Replace NA with "unidentified"
sb[,6:12] <- lapply(sb[,6:12], replace_na, replace = "unidentified")

#rename in case I need to come back
sb.mod <- sb

#Add rank columns for x axis-----
sb.mod$rank_site <- rank(sb.mod$Fourchon_rel_BJ)
sb.mod$rank_season <- rank(sb.mod$Summer_rel_Wint)

#Add percentile columns 
sb.mod$percentile_site <- cut(sb.mod$rank_site , 
                         breaks = quantile(sb.mod$rank_site, 
                                           seq(from = 0, to = 1, by = 0.1)), 
                         labels=1:10, 
                         include.lowest=TRUE)

sb.mod$percentile_season <- cut(sb.mod$rank_season , 
                         breaks = quantile(sb.mod$rank_season, 
                                           seq(from = 0, to = 1, by = 0.1)), 
                         labels=1:10, 
                         include.lowest=TRUE)

```

### Plot taxonomic ranks as pdf for browsing

#### Season

How many orders are there?
```{r}

length(unique(sb.mod$Class)) #11
#If I divide by 4, I get 3 pages

```

Create annotations

```{r}

text_high <- textGrob("Summer ", gp=gpar(fontsize=12, fontface="bold"), just = "center")
text_low <- textGrob("Winter", gp=gpar(fontsize=12, fontface="bold"), just = "center")

```

Make pdf.

```{r}

pdf("../../../../results/images/manuscript/S2_MGF_final/S2_MG_explore_fung_class_rankings_by_season.pdf")
for (i in 1:3){
  print(
    
    
    ggplot(data = sb.mod,
       aes(x = rank_season,
           y = Summer_rel_Wint,
           fill = rare_dom,
           color = rare_dom)) +
  geom_col(width = 1) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_color_manual(values = c("black", "darkgray")) +
  scale_fill_manual(values = c("black", "darkgrey")) +
  geom_vline(aes(xintercept = min(sb.mod$rank_season[sb.mod$percentile_season==10])),
             size = 0.5,
             linetype=2) +
  geom_vline(aes(xintercept = max(sb.mod$rank_season[sb.mod$percentile_season==1])),
             size = 0.5,
             linetype=2) +
  scale_x_continuous(limits = c(0, max(sb.mod$rank_season)), expand = c(0, 0)) +
  labs(y = "Differential by Season",
       x = "Rank",
       color = "Relative Abundance of Taxa",
       fill = "Relative Abundance of Taxa") +
  annotation_custom(text_low, xmin = 20, xmax = 20, ymin = -9.5, ymax = -9.5) +
  annotation_custom(text_high, xmin = 90, xmax = 90, ymin = -9.5, ymax = -9.5) +
  coord_cartesian(ylim=c(-8,3.5), clip="off") +
  geom_label_repel(inherit.aes = FALSE,
                  data = sb.mod %>%
                    filter(percentile_season %in% c(1,10)),
                  aes(x = rank_season,
                      y = Summer_rel_Wint,
                      label = Genus),
                  nudge_x = 0.5,
                  direction = "y",
                  angle = 0,
                  vjust = 0,
                  hjust = 0,
                  segment.size = 0.5) +
         facet_wrap_paginate(~ Phylum*Class, ncol = 2, nrow = 2, page = i))
  }  #end loop

dev.off()

```

### Site

Create annotations

```{r}

text_high <- textGrob("Lightly Oiled", gp=gpar(fontsize=12, fontface="bold"), just = "center")
text_low <- textGrob("Heavily Oiled", gp=gpar(fontsize=12, fontface="bold"), just = "center")

```

    
Make pdf

```{r}

pdf("../../../../results/images/manuscript/S2_MGF_final/S2_MG_explore_fung_class_rankings_by_site.pdf")
for (i in 1:3){
  print(
    ggplot(data = sb.mod,
       aes(x = rank_site,
           y = Fourchon_rel_BJ,
           fill = rare_dom,
           color = rare_dom)) +
  geom_col(width = 1) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_color_manual(values = c("black", "darkgray")) +
  scale_fill_manual(values = c("black", "darkgrey")) +
  geom_vline(aes(xintercept = min(sb.mod$rank_site[sb.mod$percentile_site==10])),
             size = 0.5,
             linetype=2) +
  geom_vline(aes(xintercept = max(sb.mod$rank_site[sb.mod$percentile_site==1])),
             size = 0.5,
             linetype=2) +
  scale_x_continuous(limits = c(0, max(sb.mod$rank_site)), expand = c(0, 0)) +
  labs(y = "Differential by Site",
       x = "Rank",
       color = "Relative Abundance of Taxa",
       fill = "Relative Abundance of Taxa") +
  annotation_custom(text_low, xmin = 20, xmax = 20, ymin = -9.5, ymax = -9.5) +
  annotation_custom(text_high, xmin = 90, xmax = 90, ymin = -9.5, ymax = -9.5) +
  coord_cartesian(ylim=c(-8,3.5), clip="off") +
  geom_label_repel(inherit.aes = FALSE,
                  data = sb.mod %>%
                    filter(percentile_site %in% c(1,10)),
                  aes(x = rank_site,
                      y = Fourchon_rel_BJ,
                      label = Genus),
                  nudge_x = 0.5,
                  direction = "y",
                  angle = 0,
                  vjust = 0,
                  hjust = 0,
                  segment.size = 0.5) +
         facet_wrap_paginate(~ Phylum*Class, ncol = 2, nrow = 2, page = i))
  }  #end loop

dev.off()

```

From the above I think I should plot:

- Dothideomycetes by site and season
- Sordariomycetes by site
- Agaricomycetes by season

As a separate figure

- Hydrocarbon degraders by site


### Plot Dothideomycetes by season

create annotations

```{r}

text_high <- textGrob("Summer \u2192", gp=gpar(fontsize=12, fontface="bold"), just = "center")
text_low <- textGrob("\u2190 Winter", gp=gpar(fontsize=12, fontface="bold"), just = "center")

```

plot

```{r}

doth.season <- ggplot(data = sb.mod %>%
         filter(Class=="Dothideomycetes"),
       aes(x = rank_season,
           y = Summer_rel_Wint,
           fill = rare_dom,
           color = rare_dom)) +
  geom_col(width = 1) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_color_manual(values = c("black", "darkgray")) +
  scale_fill_manual(values = c("black", "darkgray")) +
  geom_vline(aes(xintercept = min(sb.mod$rank_season[sb.mod$percentile_season==10])),
             size = 0.5,
             linetype=2) +
  geom_vline(aes(xintercept = max(sb.mod$rank_season[sb.mod$percentile_season==1])),
             size = 0.5,
             linetype=2) +
  scale_x_continuous(limits = c(0, max(sb.mod$rank_season)), expand = c(0, 0)) +
  labs(y = "Differential by Season",
       x = "Rank",
       title = "Dothideomycetes by Season",
       color = "Relative Abundance of Taxa",
       fill = "Relative Abundance of Taxa") +
  annotation_custom(text_low, xmin = 20, xmax = 20, ymin = -9.5, ymax = -9.5) +
  annotation_custom(text_high, xmin = 90, xmax = 90, ymin = -9.5, ymax = -9.5) +
  coord_cartesian(ylim=c(-8,3.5), clip="off") +
  geom_label_repel(inherit.aes = FALSE,
                  data = sb.mod %>%
                    filter(Class=="Dothideomycetes" & percentile_season %in% c(1,10)),
                  aes(x = rank_season,
                      y = Summer_rel_Wint,
                      label = Genus),
                  nudge_x = 0.5,
                  direction = "y",
                  angle = 0,
                  vjust = 0,
                  hjust = 0,
                  segment.size = 0.5)

```

### Dothideomycetes by site

create annotations

```{r}

text_high <- textGrob("Lightly Oiled \u2192", gp=gpar(fontsize=12, fontface="bold"), just = "center")
text_low <- textGrob("\u2190 Heavily Oiled", gp=gpar(fontsize=12, fontface="bold"), just = "center")

```

plot

```{r}

doth.site <- ggplot(data = sb.mod %>%
         filter(Class=="Dothideomycetes"),
       aes(x = rank_site,
           y = Fourchon_rel_BJ,
           fill = rare_dom,
           color = rare_dom)) +
  geom_col(width = 1) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_color_manual(values = c("black", "darkgray")) +
  scale_fill_manual(values = c("black", "darkgray")) +
  geom_vline(aes(xintercept = min(sb.mod$rank_site[sb.mod$percentile_site==10])),
             size = 0.5,
             linetype=2) +
  geom_vline(aes(xintercept = max(sb.mod$rank_site[sb.mod$percentile_site==1])),
             size = 0.5,
             linetype=2) +
  scale_x_continuous(limits = c(0, max(sb.mod$rank_site)), expand = c(0, 0)) +
  labs(y = "Differential by Site",
       x = "Rank",
       title = "Dothideomycetes by Site",
       color = "Relative Abundance of Taxa",
       fill = "Relative Abundance of Taxa") +
  annotation_custom(text_low, xmin = 20, xmax = 20, ymin = -9.5, ymax = -9.5) +
  annotation_custom(text_high, xmin = 90, xmax = 90, ymin = -9.5, ymax = -9.5) +
  coord_cartesian(ylim=c(-8,3.5), clip="off") +
  geom_label_repel(inherit.aes = FALSE,
                  data = sb.mod %>%
                    filter(Class=="Dothideomycetes" & percentile_site %in% c(1,10)),
                  aes(x = rank_site,
                      y = Fourchon_rel_BJ,
                      label = Genus),
                  nudge_x = 0.5,
                  direction = "y",
                  angle = 0,
                  vjust = 0,
                  hjust = 0,
                  segment.size = 0.5)

```


plot all top of figure

```{r}

doth.all <- plot_grid(doth.site, doth.season)

```


### Agaricomycetes by season

create annotations

```{r}

text_high <- textGrob("Summer \u2192", gp=gpar(fontsize=12, fontface="bold"), just = "center")
text_low <- textGrob("\u2190 Winter", gp=gpar(fontsize=12, fontface="bold"), just = "center")

```

plot

```{r}

agarico <- ggplot(data = sb.mod %>%
         filter(Class=="Agaricomycetes"),
       aes(x = rank_season,
           y = Summer_rel_Wint,
           fill = rare_dom,
           color = rare_dom)) +
  geom_col(width = 1) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_color_manual(values = c("black", "darkgray")) +
  scale_fill_manual(values = c("black", "darkgray")) +
  geom_vline(aes(xintercept = min(sb.mod$rank_season[sb.mod$percentile_season==10])),
             size = 0.5,
             linetype=2) +
  geom_vline(aes(xintercept = max(sb.mod$rank_season[sb.mod$percentile_season==1])),
             size = 0.5,
             linetype=2) +
  scale_x_continuous(limits = c(0, max(sb.mod$rank_season)), expand = c(0, 0)) +
  labs(y = "Differential by Season",
       x = "Rank",
       title = "Agaricomycetes",
       color = "Relative Abundance of Taxa",
       fill = "Relative Abundance of Taxa") +
  annotation_custom(text_low, xmin = 20, xmax = 20, ymin = -9.5, ymax = -9.5) +
  annotation_custom(text_high, xmin = 90, xmax = 90, ymin = -9.5, ymax = -9.5) +
  coord_cartesian(ylim=c(-8,3.5), clip="off") +
  geom_label_repel(inherit.aes = FALSE,
                  data = sb.mod %>%
                    filter(Class=="Agaricomycetes" & percentile_season %in% c(1,10)),
                  aes(x = rank_season,
                      y = Summer_rel_Wint,
                      label = Genus),
                  nudge_x = 0.5,
                  direction = "y",
                  angle = 0,
                  vjust = 0,
                  hjust = 0,
                  segment.size = 0.5)

```

### Sordariomycetes by site

create annotations

```{r}

text_high <- textGrob("Lightly Oiled \u2192", gp=gpar(fontsize=12, fontface="bold"), just = "center")
text_low <- textGrob("\u2190 Heavily Oiled", gp=gpar(fontsize=12, fontface="bold"), just = "center")

```

plot

```{r}

sordario <- ggplot(data = sb.mod %>%
         filter(Class=="Sordariomycetes"),
       aes(x = rank_site,
           y = Fourchon_rel_BJ,
           fill = rare_dom,
           color = rare_dom)) +
  geom_col(width = 1) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_color_manual(values = c("black", "darkgray")) +
  scale_fill_manual(values = c("black", "darkgray")) +
  geom_vline(aes(xintercept = min(sb.mod$rank_site[sb.mod$percentile_site==10])),
             size = 0.5,
             linetype=2) +
  geom_vline(aes(xintercept = max(sb.mod$rank_site[sb.mod$percentile_site==1])),
             size = 0.5,
             linetype=2) +
  scale_x_continuous(limits = c(0, max(sb.mod$rank_site)), expand = c(0, 0)) +
  labs(y = "Differential by Site",
       x = "Rank",
       title = "Sordariomycetes",
       color = "Relative Abundance of Taxa",
       fill = "Relative Abundance of Taxa") +
  annotation_custom(text_low, xmin = 20, xmax = 20, ymin = -9.5, ymax = -9.5) +
  annotation_custom(text_high, xmin = 90, xmax = 90, ymin = -9.5, ymax = -9.5) +
  coord_cartesian(ylim=c(-8,3.5), clip="off") +
  geom_label_repel(inherit.aes = FALSE,
                  data = sb.mod %>%
                    filter(Class=="Sordariomycetes" & percentile_site %in% c(1,10)),
                  aes(x = rank_site,
                      y = Fourchon_rel_BJ,
                      label = Genus),
                  nudge_x = 0.5,
                  direction = "y",
                  angle = 0,
                  vjust = 0,
                  hjust = 0,
                  segment.size = 0.5)

```

### Plot and save figure 4

```{r}

plot_grid(doth.site + labs(title = NULL,subtitle = "Dothideomycetes"), doth.season + labs(title = NULL,subtitle = "Dothideomycetes"), sordario + labs(title = NULL,subtitle = "Sordarioomycetes"), agarico + labs(title = NULL,subtitle = "Agaricomycetes"), labels = c("a", "b", "c", "d"))

ggsave("../../../../results/images/manuscript/S2_MGF_final/S2_MGF_Fig4.png", width = 10, height = 8, units = "in")

```

### Venn Diagram

Plot and save. To help me visualize taxa overlap.

```{r}

sb.mod.dom <- sb.mod %>%
  filter(rare_dom=="dominant")

#Site and Season extremes
venn.list <- list('Heavily Oiled' = sb.mod.dom$featureid[sb.mod.dom$percentile_site==1],
                  Winter = sb.mod.dom$featureid[sb.mod.dom$percentile_season==1],
                  Summer = sb.mod.dom$featureid[sb.mod.dom$percentile_season==10],
                  'Lightly Oiled' = sb.mod.dom$featureid[sb.mod.dom$percentile_site==10])

venn(venn.list, box = FALSE, ggplot = TRUE, ellipse = TRUE, )

ggsave("../../../../results/images/manuscript/S2_MG_fungi_venn.png", width = 5, height = 5, units = "in")

lapply(venn.list, length)

```


### Make Table of Extremely Ranked Taxa

```{r}

x.tax <- plyr:::ldply(venn.list, data.frame)

x.taxon <- sb.mod[match(x.tax$X..i.., sb.mod$featureid),] %>%
  select(Phylum, Class, Order, Family, Genus, Species)

x.all <- cbind(x.tax, x.taxon)

names(x.all) <- c("Associate", "OTU id", "Phylum", "Class", "Order", "Family", "Genus", "Species")

#They match, but a .1 was added to duplicates
x.all$X..i..[which(x.all$X..i..!=rownames(x.taxon))]
rownames(x.taxon)[which(x.all$X..i..!=rownames(x.taxon))]

write.csv(x.all, "../../../../results/images/manuscript/S2_MGF_final/S2_MGF_extreme_ranks.table.csv", row.names = FALSE)

```

### Overview of Taxa by % OTUs

```{r}

sb.mod %>%
  group_by(Phylum) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

```

### Percent by reads

```{r}

fid <- prune_taxa(sb.mod$featureid, fung.2season_with_outliers) 
sb.mod$tax.sums <- fid %>%
  taxa_sums() 

sb.mod %>%
  group_by(Phylum) %>%
  summarise (n = sum(tax.sums)) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

```

### Taxa that are positively associated with Heavily Oiled site


```{r}

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1) %>%
  group_by(Phylum) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1) %>%
  group_by(Phylum, Class) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq)) %>%
  print.data.frame()

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1) %>%
  group_by(Family) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq)) %>%
  print.data.frame()

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1) %>%
  group_by(Family, Genus) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq)) %>%
  print.data.frame()
```


### Taxa that are positively associated with Heavily Oiled site and Summer

```{r}

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1 &
           percentile_season==10) %>%
  group_by(Phylum) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1 &
           percentile_season==10) %>%
  group_by(Phylum, Class) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1 &
           percentile_season==10) %>%
  group_by(Family) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1 &
           percentile_season==10) %>%
  group_by(Family, Genus) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

```

### Taxa that are positively associated with Heavily Oiled site and Winter

```{r}

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1 &
           percentile_season==1) %>%
  group_by(Phylum) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1 &
           percentile_season==1) %>%
  group_by(Phylum, Class) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1 &
           percentile_season==1) %>%
  group_by(Family) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==1 &
           percentile_season==1) %>%
  group_by(Class,Family, Genus) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

```

### Taxa that are positively associated with Lightly Oiled site

```{r}

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10) %>%
  group_by(Phylum) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10) %>%
  group_by(Phylum, Class) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq)) %>%
  print.data.frame()

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10) %>%
  group_by(Family) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq)) %>%
  print.data.frame()

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10) %>%
  group_by(Genus) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq)) %>%
  print.data.frame()

```


### Taxa that are positively associated with Lightly Oiled site and Summer

```{r}

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10 &
           percentile_season==10) %>%
  group_by(Phylum) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10 &
           percentile_season==10) %>%
  group_by(Phylum, Class) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10 &
           percentile_season==10) %>%
  group_by(Family) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10 &
           percentile_season==10) %>%
  group_by(Family, Genus) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

```

### Taxa that are positively associated with Lightly Oiled site and Winter

```{r}

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10 &
           percentile_season==1) %>%
  group_by(Phylum) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10 &
           percentile_season==1) %>%
  group_by(Phylum, Class) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10 &
           percentile_season==1) %>%
  group_by(Family) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))

sb.mod %>%
  filter(rare_dom=="dominant" &
           percentile_site==10 &
           percentile_season==1) %>%
  group_by(Class,Family, Genus) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  arrange(desc(freq))
  
```
  