---
title: "S2_MGF Oil and alpha diversity"
author: "Stephen Formel"
date: "12/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, out.width = "100%")
```

### S2_MGF Manuscript  Oil and Alpha Diversity

Last updated 4 Dec 2020 by Steve Formel

Description:   Is there a relationship between diversity of salt marsh soil microbial communities and oil abundance?

### Load libraries

```{r message = FALSE}

library(cowplot)
library(tidyverse)
library(brms)

```

### Load and Clean data

Here I use a convenient phyloseq function to generate all three metrics.

```{r}

source("./S2_MGF_load_packages_and_clean_data.R")

p <- plot_richness(fung.2season_with_outliers)

#convert value to Hill numbers

p1 <- p$data
p1$hill_value <- NA

p1$value[which(p1$variable == "Observed")] <- p1$value[which(p1$variable == "Observed")]

p1$value[which(p1$variable == "Shannon")] <- exp(p1$value[which(p1$variable == "Shannon")])

p1$value[which(p1$variable == "Simpson")] <- 1/(1 - p1$value[which(p1$variable == "Simpson")])

p1$hill_order <- NA

p1$hill_order[which(p1$variable == "Observed")] <- 0
p1$hill_order[which(p1$variable == "Shannon")] <- 1
p1$hill_order[which(p1$variable == "Simpson")] <- 2

#rename levels for site
p1$site <- as.factor(p1$site)
levels(p1$site) <- plyr:::revalue(levels(p1$site), c("BJ" = "Heavily Oiled", "F" = "Lightly Oiled"))

#total PAHs----
p1 <- p1 %>%
  filter(variable %in% c("Observed", "Shannon", "Simpson")) %>%
  droplevels()

p.list <- split.data.frame(x = p1, f = p1$variable)

#also for plotting ultimate figure
p.fung <-p.list

```

### Bayesian LM of alpha diversity against total relevant PAHs

based on  https://solomonkurz.netlify.app/post/robust-linear-regression-with-the-robust-student-s-t-distribution/
and https://bayesed-and-confused.netlify.app/post/model-fit-checks/

I look at the models as they're generated and ultimately create a table of beta and R-squared values.

### Hill Order = 0

This is the equivalent of richness.

```{r}

f0 <- brm(value ~ Total.relevant.PAHs, 
          data = p.list[[1]],
          family = "gaussian",
          chains = 4, cores = 4,
          seed = 1)

M <- f0
pp_check(object = M, type = "dens_overlay", nsamples = 100)
pp_check(M, type = "stat", stat = 'median', nsamples = 100)
pp_check(M, type = "stat", stat = 'mean', nsamples = 100)
pp_check(M,type = 'intervals')

plot(M)
summ <- as.data.frame(posterior_summary(M))

#####R2
r2 <- as.data.frame(bayes_R2(object = M,resp = NULL,summary = TRUE,robust = FALSE,probs = c(0.025, 0.975)))

#get parameters for plotting
df.plot <- rbind(summ[2,], r2[1,])
df.plot$hill_order <- "0"
df.plot$param <- rownames(df.plot)

df.plot.done <- df.plot

```

### Hill Order = 1

This is the equivalent of Shannon Diversity.

```{r}

f1 <- brm(value ~ Total.relevant.PAHs, 
          data = p.list[[2]],
          family = "skew_normal",
          chains = 4, cores = 4,
          seed = 1)

M <- f1
pp_check(object = M, type = "dens_overlay", nsamples = 100)
pp_check(M, type = "stat", stat = 'median', nsamples = 100)
pp_check(M, type = "stat", stat = 'mean', nsamples = 100)
pp_check(M,type = 'intervals')

plot(M)
summ <- as.data.frame(posterior_summary(M))

#R2
r2 <- as.data.frame(bayes_R2(object = M,resp = NULL,summary = TRUE,robust = FALSE,probs = c(0.025, 0.975)))

#get parameters for plotting
df.plot <- rbind(summ[2,], r2[1,])
df.plot$hill_order <- "1"
df.plot$param <- rownames(df.plot)

df.plot.done <- rbind(df.plot.done, df.plot)

```

### Hill Order = 2

This is the equivalent of Simposon Diversity.

```{r}

f2 <- brm(value ~ Total.relevant.PAHs, 
                data = p.list[[3]],
                family = "skew_normal",
                chains = 4, cores = 4,
                seed = 1,
          control = list(adapt_delta = 0.99))

M <- f2
pp_check(object = M, type = "dens_overlay", nsamples = 100)
pp_check(M, type = "stat", stat = 'median', nsamples = 100)
pp_check(M, type = "stat", stat = 'mean', nsamples = 100)
pp_check(M,type = 'intervals')

plot(M)
print(M)
summ <- as.data.frame(posterior_summary(M))

#R2
r2 <- as.data.frame(bayes_R2(object = M,resp = NULL,summary = TRUE,robust = FALSE,probs = c(0.025, 0.975)))

#get parameters for plotting
df.plot <- rbind(summ[2,], r2[1,])
df.plot$hill_order <- "2"
df.plot$param <- rownames(df.plot)

```

### Look at table

```{r}

df.plot.done <- rbind(df.plot.done, df.plot)
df.plot.done$microbe <- "Fungi"
fungi.plot.done <- df.plot.done

plot.params.df <- fungi.plot.done

plot.params.df

```


### Write table

```{r}
write.csv(plot.params.df, "../../../../results/images/manuscript/S2_MGF_final/S2_MGF_oil_div_results.csv")

```

