---
title: "S2_MGF Oil Stats"
author: "Stephen Formel"
date: "12/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width = "100%")
```

### S2_MG Manuscript

Last updated 6 Dec 2020 by Steve Formel

Figure 1 stats:  model of PAHs between site and season
Description:   Do our results match our experimental strategy? Are there gradients of oil within each site and a large difference between sites?

### Load Libraries

```{r}

library(tidyverse)
library(compositions)
library(ggplot2)
library(cowplot)

```

### Load and Clean data

```{r, message = FALSE}

source("./S2_MGF_load_packages_and_clean_data.R")

voi <- fung.2season_with_outliers

df <- data.frame(sample_data(voi)) %>%
  select(SampleID,
         site,
         season,
         Total.C1.C3.chrysenes,
         Total.C1.C4.naphthalenes,
         Total.C1.C4.phenanthrenes,
         Total.C1.C3.dibenzothiophenes,
         Total.relevant.PAHs)

#relabel levels
df$site <- as.factor(df$site)
levels(df$site) <- plyr:::revalue(levels(df$site), c("BJ" = "Heavily Oiled", "F" = "Lightly Oiled"))

df$season <- as.factor(df$season)
levels(df$season) <- plyr:::revalue(levels(df$season), c("WINTER" = "Winter", "SUMMER" = "Summer"))

#reorder
levels(df$season) <- c("Winter", "Summer")


```
### Make colorblind-safe palette

```{r}

cPAL <- c("#E69F00", "#0072B2")

```

### Notes

http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.876.3979&rep=rep1&type=pdf

good explanations and tutorial
https://cran.r-project.org/web/packages/compositions/vignettes/UsingCompositions.pdf

### Explore data

Histogram of total PAHs

```{r}

df %>% 
  ggplot(aes(x = Total.relevant.PAHs)) + 
  geom_histogram() +
  scale_x_log10()

df$PAH_bin <- cut(df$Total.relevant.PAHs, 
                  breaks = c(0,0.1,1,10,100,1000), 
                  labels = c("Less than 0.1",
                             "0.1 to 1",
                             "1 to 10",
                             "10 to 100",
                             "100 to 1000")) 

df %>% 
  group_by(PAH_bin) %>% 
  summarise(n = n())

#0.1 to 10 = 63 + 11 = 74 --> 74/82

```

Relative abundance of each PAH class.
```{r}

#This transforms each number into it's relative abundance in that sample
comps <- acomp(df[,c(4:7)])

clr.df <- cbind(comps, df)

clr.df.gathered <- clr.df %>%
  gather(key = "PAH", value = "Proportion", c(1:4))

clr.df.gathered %>%
  ggplot(aes(x = PAH,
             y = Proportion,
             color = PAH)) +
  geom_boxplot() +
  facet_grid(rows = vars(site),
             cols = vars(season))

```

  
But as I understand it, it's inappropriate to do the stats on this because it's closed.  Need to translate to CLR.

### CLR-transformation

CLR-transform data and perform PCA with Euclidean distance.  This transformation + distance is known as Aitchison distance.

```{r}

clr.PAH <- clr(na.omit(df[,c(4:7)]))
pc <- princomp(x = clr.PAH)

pc$Loadings # The loadings as compositional vector
pc$loadings # The loadings in clr-space
df.pca <- pc$scores

aitchison.pca.plot <- cbind(na.omit(df), df.pca) %>%
  ggplot(aes(x = Comp.1,
             y = Comp.2,
             fill = season,
             shape = site)) +
  geom_point(size = 4,
             stroke = 1,
             color = "black") +
  scale_fill_manual(values = cPAL) +
  scale_shape_manual(values = c(21,24)) +
  labs(fill = "Season",
       shape = "Site") +
  theme_bw() +
  theme(legend.position = "bottom", legend.box="vertical") +
  guides(fill=guide_legend(override.aes=list(shape=21)))

```

### PERMANOVA

```{r}

clr.PAH <- clr(na.omit(df[,c(4:7)]))
clr.PAH <- as.data.frame(clr.PAH)

df.na <- na.omit(df) %>%
  select(SampleID, site, season)

df.clr <- cbind(df.na, clr.PAH)

set.seed(1)
adonis(formula = clr.PAH ~ site*season, data = df.na, permutations = 9999, method = "euclidean")

```

#Boxplot of PAH composition

```{r}

CLR.boxplot <- df.clr %>%
  gather(key = "PAH", value = "clr_val", Total.C1.C3.chrysenes:Total.C1.C3.dibenzothiophenes) %>%
  ggplot(aes(x = PAH,
         y = clr_val),
         color = "black") +
  geom_boxplot(aes(fill = season),
         alpha = 0.5) +
  facet_grid(rows = vars(site), cols = vars(season)) +
  theme_bw() +
  scale_fill_manual(values = cPAL) +
  scale_x_discrete(labels = c("chrysenes", "dibenzothiophenes", "naphthalenes", "phenanthrenes")) +
  labs(y = "Centered Log-Ratio") +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1))

```


## Fig S1

PCA of PAH composition based on Aitchison distance and boxplot of clr-transformed PAH composition.

```{r}

plot_grid(aitchison.pca.plot, CLR.boxplot, labels = c("a", "b"))

```


### Save to file

```{r}

ggsave("../../../../results/images/manuscript/S2_MGF_final/S2_MGF_S1_PAH_comp.png", width = 10, height = 6, units = "in")

```

