---
title: "S2_MGF Mantel Tests"
author: "Stephen Formel"
date: "11/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, out.width = "100%")
```

### S2_MGF Manuscript  Mantel Tests
#by Steve Formel

Description: Is there spatial autocorrelation with oil or community composition?

_Note that winter = time point 1 and summer = time point 2.  This is leftover from earilier analyses.  I was asked to change these terms in the manuscript revisions, and I didn't have time to completely revise the scripts._

### Load libraries

```{r message = FALSE}

library(tidyverse)
library(vegan)
library(ecodist)
library(geosphere)
library(compositions)

```

### Load and Clean data

```{r}

source("./S2_MGF_load_packages_and_clean_data.R")

#Subset unfiltered

fung.2season.BJ.summer.unfiltered <- fung.2season.not_filtered %>%
  subset_samples( . , (site %in% c("BJ") & season %in% c("SUMMER"))) %>%
  {prune_taxa(taxa_sums(.) > 0 , .)}

fung.2season.BJ.winter.unfiltered <- fung.2season.not_filtered %>%
  subset_samples( . , (site %in% c("BJ") & season %in% c("WINTER"))) %>%
  {prune_taxa(taxa_sums(.) > 0 , .)}

fung.2season.F.summer.unfiltered <- fung.2season.not_filtered %>%
  subset_samples( . , (site %in% c("F") & season %in% c("SUMMER"))) %>%
  {prune_taxa(taxa_sums(.) > 0 , .)}

fung.2season.F.winter.unfiltered <- fung.2season.not_filtered %>%
  subset_samples( . , (site %in% c("F") & season %in% c("WINTER"))) %>%
  {prune_taxa(taxa_sums(.) > 0 , .)}


#Get list of all fungal phyloseq objects
varnames <- c("fung.2season.F.summer_with_outliers", 
              "fung.2season.F.winter_with_outliers", 
              "fung.2season.BJ.summer_with_outliers", 
              "fung.2season.BJ.winter_with_outliers")

varnames.filtered <- c("fung.2season.F.summer.unfiltered", 
                       "fung.2season.F.winter.unfiltered", 
                       "fung.2season.BJ.summer.unfiltered",
                       "fung.2season.BJ.winter.unfiltered")

#make empty matrix
B <- matrix(ncol = 4, nrow = length(varnames))

```

### Mantel tests

#### Bray-Curtis

```{r}

for (i in 1:length(varnames)) {
  
  voi <- get(varnames[i])
  df <- t(data.frame(otu_table(voi)))
  df <- data.frame(df)
  
  df.env.na <- voi %>%
    sample_data() %>%
    data.frame() %>%
    select(SampleID,
           site,
           season,
           Latitude,
           Longitude) %>%
    na.omit()
  df.na <- df[df.env.na$SampleID,]
  dist.df <- vegdist(df.na, method = "bray") 
  
  #make distance metric based on lat long
  mtx <- as.matrix(data.frame(df.env.na$Longitude, df.env.na$Latitude))
  
  #create distance matrix
  mat <- as.dist(distm(mtx, fun=distVincentyEllipsoid))
  
  #note that this is calling the eocdist version, not the vegan version
  man.results <- mantel(dist.df ~ mat)    
  man.results[7] <- ifelse(man.results[4] <= 0.05, "significant", "not signficant")
  
  B[i,] <- c("object_name" = varnames[i], man.results[c(1,4)], "result" = man.results[c(7)])
}

#add names and make into data frame
colnames(B) <- c("object_name", "mantel.stat(r)", "p-value", "results")
C <- as.data.frame(B) 

#view results
C[(C$results=="significant"),] 

#sort by signficance
C <- C[order(C$results=="significant", decreasing = TRUE),]

```

##### Print and save

```{r}

print(C, row.names = FALSE)

#write.csv(x = C,file = "../../../../results/images/manuscript/S2_MGF_final/S2_MGF_mantel_comm_comp_bray-curtis.csv", row.names = FALSE)

```

#### Jaccard Index

```{r}

for (i in 1:length(varnames)) {
  
  voi <- get(varnames[i])
  df <- t(data.frame(otu_table(voi)))
  df <- data.frame(df)
  
  df.env.na <- voi %>%
    sample_data() %>%
    data.frame() %>%
    select(SampleID,
           site,
           season,
           Latitude,
           Longitude) %>%
    na.omit()
  df.na <- df[df.env.na$SampleID,]
  dist.df <- vegdist(df.na, method = "jaccard", binary = TRUE) 
  
  #make distance metric based on lat long
  mtx <- as.matrix(data.frame(df.env.na$Longitude, df.env.na$Latitude))
  
  #create distance matrix
  mat <- as.dist(distm(mtx, fun=distVincentyEllipsoid))
  
  #note that this is calling the eocdist version, not the vegan version
  man.results <- mantel(dist.df ~ mat)    
  man.results[7] <- ifelse(man.results[4] <= 0.05, "significant", "not signficant")
  
  B[i,] <- c("object_name" = varnames[i], man.results[c(1,4)], "result" = man.results[c(7)])
}

#add names and make into data frame
colnames(B) <- c("object_name", "mantel.stat(r)", "p-value", "results")
C <- as.data.frame(B) 

#view results
C[(C$results=="significant"),] 

#sort by signficance
C <- C[order(C$results=="significant", decreasing = TRUE),]

```

##### Print and save

```{r}

print(C, row.names = FALSE)

#write.csv(x = C,file = "../../../../results/images/manuscript/S2_MGF_final/S2_MGF_mantel_comm_comp_jaccard.csv", row.names = FALSE)

```

#### Aitchison Distance

```{r}

for (i in 1:length(varnames)) {
  
  voi <- get(varnames[i])
  df <- t(data.frame(otu_table(voi)))
  df <- data.frame(df)
  
  df.env.na <- voi %>%
    sample_data() %>%
    data.frame() %>%
    select(SampleID,
           site,
           season,
           Latitude,
           Longitude) %>%
    na.omit()

  df.na <- df[df.env.na$SampleID,]
  
  clr.df <- clr(df.na)
  clr.df <- as.data.frame(clr.df)
  
  dist.df <- vegdist(clr.df, method = "euclidean") 
  
  #make distance metric based on lat long
  mtx <- as.matrix(data.frame(df.env.na$Longitude, df.env.na$Latitude))
  
  #create distance matrix
  mat <- as.dist(distm(mtx, fun=distVincentyEllipsoid))
  
  #note that this is calling the eocdist version, not the vegan version
  man.results <- mantel(dist.df ~ mat)    
  man.results[7] <- ifelse(man.results[4] <= 0.05, "significant", "not signficant")
  
  B[i,] <- c("object_name" = varnames[i], man.results[c(1,4)], "result" = man.results[c(7)])
}

#add names and make into data frame
colnames(B) <- c("object_name", "mantel.stat(r)", "p-value", "results")
C <- as.data.frame(B) 

#view results
C[(C$results=="significant"),] 

#sort by signficance
C <- C[order(C$results=="significant", decreasing = TRUE),]

```

##### Print and save

```{r}

print(C, row.names = FALSE)

#write.csv(x = C,file = "../../../../results/images/manuscript/S2_MGF_final/S2_MGF_mantel_comm_comp_aitchison.csv", row.names = FALSE)

```

### Spatial autocorrelation of PAHs

I collapse PAHs into Aitchison distance, like I've done for other tests.

```{r}

#make empty matrix
B <- matrix(ncol = 4, nrow = length(varnames))

for (i in 1:length(varnames)) {
  
  voi <- get(varnames[i])
  df.env.na <- data.frame(sample_data(voi)) %>%
  select(SampleID,
         site,
         season,
         Total.C1.C3.chrysenes,
         Total.C1.C4.naphthalenes,
         Total.C1.C4.phenanthrenes,
         Total.C1.C3.dibenzothiophenes,
         Latitude,
         Longitude) %>%
    na.omit()
  
  clr.PAH <- clr(na.omit(df.env.na[,c(4:7)]))
  clr.PAH <- as.data.frame(clr.PAH)

  dist.df <- vegdist(clr.PAH, method = "euclidean")
  
  #make distance metric based on lat long
  mtx <- as.matrix(data.frame(df.env.na$Longitude, df.env.na$Latitude))
  
  # create distance matrix
  mat <- as.dist(distm(mtx, fun=distVincentyEllipsoid))
  
  #note that this is calling the eocdist version, not the vegan version
  man.results <- mantel(dist.df ~ mat)    

    man.results[7] <- ifelse(man.results[4] <= 0.05, "significant", "not signficant")
  
  B[i,] <- c("object_name" = varnames[i], man.results[c(1,4)], "result" = man.results[c(7)])
  
}

#add names and make into data frame
colnames(B) <- c("object_name", "mantel.stat(r)", "p-value", "results")
C <- as.data.frame(B) 

#view results
C[(C$results=="significant"),] 

#sort by signficance
C <- C[order(C$results=="significant", decreasing = TRUE),]

```

##### Print and save

```{r}

print(C, row.names = FALSE)

#rite.csv(x = C,file = "../../../../results/images/manuscript/S2_MGF_final/S2_MGF_mantel_oil.csv", row.names = FALSE)

```

## How does it look when rare taxa are filtered out?

#### Bray-Curtis

```{r}

for (i in 1:length(varnames.filtered)) {
  
  voi <- get(varnames.filtered[i])
  df <- t(data.frame(otu_table(voi)))
  df <- data.frame(df)
  
  df.env.na <- voi %>%
    sample_data() %>%
    data.frame() %>%
    select(SampleID,
           site,
           season,
           Latitude,
           Longitude) %>%
    na.omit()
  df.na <- df[df.env.na$SampleID,]
  dist.df <- vegdist(df.na, method = "bray") 
  
  #make distance metric based on lat long
  mtx <- as.matrix(data.frame(df.env.na$Longitude, df.env.na$Latitude))
  
  #create distance matrix
  mat <- as.dist(distm(mtx, fun=distVincentyEllipsoid))
  
  #note that this is calling the eocdist version, not the vegan version
  man.results <- mantel(dist.df ~ mat)    
  man.results[7] <- ifelse(man.results[4] <= 0.05, "significant", "not signficant")
  
  B[i,] <- c("object_name" = varnames.filtered[i], man.results[c(1,4)], "result" = man.results[c(7)])
}

#add names and make into data frame
colnames(B) <- c("object_name", "mantel.stat(r)", "p-value", "results")
C <- as.data.frame(B) 

#view results
C[(C$results=="significant"),] 

#sort by signficance
C <- C[order(C$results=="significant", decreasing = TRUE),]

```

##### Print and save

```{r}

print(C, row.names = FALSE)

#write.csv(x = C,file = "../../../../results/images/manuscript/S2_MGF_final/S2_MGF_mantel_comm_comp_bray-curtis_filtered.csv", row.names = FALSE)

```

#### Jaccard Index

```{r}

for (i in 1:length(varnames.filtered)) {
  
  voi <- get(varnames.filtered[i])
  df <- t(data.frame(otu_table(voi)))
  df <- data.frame(df)
  
  df.env.na <- voi %>%
    sample_data() %>%
    data.frame() %>%
    select(SampleID,
           site,
           season,
           Latitude,
           Longitude) %>%
    na.omit()
  df.na <- df[df.env.na$SampleID,]
  dist.df <- vegdist(df.na, method = "jaccard", binary = TRUE) 
  
  #make distance metric based on lat long
  mtx <- as.matrix(data.frame(df.env.na$Longitude, df.env.na$Latitude))
  
  #create distance matrix
  mat <- as.dist(distm(mtx, fun=distVincentyEllipsoid))
  
  #note that this is calling the eocdist version, not the vegan version
  man.results <- mantel(dist.df ~ mat)    
  man.results[7] <- ifelse(man.results[4] <= 0.05, "significant", "not signficant")
  
  B[i,] <- c("object_name" = varnames.filtered[i], man.results[c(1,4)], "result" = man.results[c(7)])
}

#add names and make into data frame
colnames(B) <- c("object_name", "mantel.stat(r)", "p-value", "results")
C <- as.data.frame(B) 

#view results
C[(C$results=="significant"),] 

#sort by signficance
C <- C[order(C$results=="significant", decreasing = TRUE),]

```

##### Print and save

```{r}

print(C, row.names = FALSE)

#write.csv(x = C,file = "../../../../results/images/manuscript/S2_MGF_final/S2_MGF_mantel_comm_comp_jaccard_filtered.csv", row.names = FALSE)

```

#### Aitchison Distance

```{r}

for (i in 1:length(varnames.filtered)) {
  
  voi <- get(varnames.filtered[i])
  df <- t(data.frame(otu_table(voi)))
  df <- data.frame(df)
  
  df.env.na <- voi %>%
    sample_data() %>%
    data.frame() %>%
    select(SampleID,
           site,
           season,
           Latitude,
           Longitude) %>%
    na.omit()

  df.na <- df[df.env.na$SampleID,]
  
  clr.df <- clr(df.na)
  clr.df <- as.data.frame(clr.df)
  
  dist.df <- vegdist(clr.df, method = "euclidean") 
  
  #make distance metric based on lat long
  mtx <- as.matrix(data.frame(df.env.na$Longitude, df.env.na$Latitude))
  
  #create distance matrix
  mat <- as.dist(distm(mtx, fun=distVincentyEllipsoid))
  
  #note that this is calling the eocdist version, not the vegan version
  man.results <- mantel(dist.df ~ mat)    
  man.results[7] <- ifelse(man.results[4] <= 0.05, "significant", "not signficant")
  
  B[i,] <- c("object_name" = varnames.filtered[i], man.results[c(1,4)], "result" = man.results[c(7)])
}

#add names and make into data frame
colnames(B) <- c("object_name", "mantel.stat(r)", "p-value", "results")
C <- as.data.frame(B) 

#view results
C[(C$results=="significant"),] 

#sort by signficance
C <- C[order(C$results=="significant", decreasing = TRUE),]

```

##### Print and save

```{r}

print(C, row.names = FALSE)

#write.csv(x = C,file = "../../../../results/images/manuscript/S2_MGF_final/S2_MGF_mantel_comm_comp_aitchison_filtered.csv", row.names = FALSE)

```