---
title: 'S2_MGF Figure 3: Beta Diversity'
author: "Stephen Formel"
date: "11/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width = "100%")
```

### S2_MGF Manuscript  Figure 3 - beta diversity
#by Steve Formel

Description:   multSE, NMDS, PERMANOVA, and dbRDA with oil

_Note that winter = time point 1 and summer = time point 2.  This is leftover from earilier analyses.  I was asked to change these terms in the manuscript revisions, and I didn't have time to completely revise the scripts._

### Load libraries

```{r message = FALSE}

library(tidyverse)
library(cowplot)
library(devtools)
library(compositions)

```


### Load and Clean data

```{r, message = FALSE}

source("./S2_MGF_load_packages_and_clean_data.R")

```

### Color palette

```{r}

cPAL <- c("#E69F00", "#0072B2")

```


### Load custom function for multSE

From Jon Lefcheck github 

https://jonlefcheck.net/2015/03/31/how-much-is-enough-a-new-technique-for-quantifying-precision-of-community-surveys/

```{r}

multSE <- source_url("https://raw.githubusercontent.com/jslefche/multSE/master/R/multSE.R")[[1]]

```

### Run multSE

```{r}

Sys.time()
voi <- fung.2season_with_outliers
voi.dm <- distance(voi, method = "bray")
out.multiSE.fungi <- multSE(mat = voi.dm, 
                      group = sample_data(voi)$site_season, 
                      nresamp = 10000, 
                      permanova = FALSE)
Sys.time()

#took about 1 min

out.multiSE.fungi$site <- c(rep("Bay Jimmy", 39), rep("Fourchon", 46))
out.multiSE.fungi$season <- c(rep("Time Point 1", 20), rep("Time Point 2", 42), rep("Time Point 1", 23))

```

### Plot multSE

```{r}

multSE.plot <- ggplot(out.multiSE.fungi, aes(x = n.samp, 
                                             y = means,
                                             shape = site,
                                             fill = season)) +
  geom_errorbar(aes(ymax = upper.ci, 
                    ymin = lower.ci), 
                width = 0.2) +
  geom_point() + 
  theme(legend.text = element_text(size = 10) ) +
  scale_shape_manual(values = c(21, 24)) +
  scale_fill_manual(values = cPAL) +
  scale_x_continuous(breaks = seq(from = 0, to = 25, by = 5)) +
  #guides(shape = guide_legend(override.aes = list(size = 5))) +
  coord_cartesian(ylim = c(0, 1)) +
  theme_bw(base_size = 14) +
  facet_grid(rows = vars(season),
             cols = vars(site)) +
  labs(x = "Sample size (n)", 
       y = "Multivariate pseudo SE",
       shape = "Site",
       fill = "Time Point")
  #theme(legend.position = c(0.8, 0.8), 
  #      panel.grid.minor = element_blank(),
  #      legend.box.background = element_rect(colour = "black")) 

```

### Plot NMDS

```{r, message = FALSE}

voi <- fung.2season_with_outliers

fung.ord <- ordinate(voi, method = "NMDS", distance = "bray")

#put together data
plot.df <- data.frame(sample_data(voi), fung.ord$points)

#relabel levels
plot.df$site <- as.factor(plot.df$site)
levels(plot.df$site) <- plyr:::revalue(levels(plot.df$site), c("BJ" = "Bay Jimmy", "F" = "Fourchon"))

plot.df$season <- as.factor(plot.df$season)
levels(plot.df$season) <- plyr:::revalue(levels(plot.df$season), c("SUMMER" = "Time Point 2", "WINTER" = "Time Point 1"))

#plot
fung.NMDS.plot <- ggplot(data = plot.df,
                        aes(x = MDS1,
                            y = MDS2,
                            shape = site,
                          fill = season)) +
  geom_point(size = 3,
             stroke = 0.5,
             color = "black") +
  scale_shape_manual(values = c(21, 24)) +
  scale_fill_manual(values = cPAL) + 
  theme_bw(base_size = 14) +
  theme_bw() +
  labs(x = "NMDS1",
       y = "NMDS2",
       color = "Time Point",
       shape = "Site",
       caption = paste0("Stress = ", round(fung.ord$stress, 2))) +
  theme(legend.text = element_text(size = 10),
        legend.position = "right") +
  guides(shape = guide_legend(override.aes = list(size = 5)),
         fill = guide_legend(override.aes = list(size = 5, shape=21)))

```

### Plot both together and save

```{r}

plot_grid(multSE.plot + theme(legend.position = "none"), fung.NMDS.plot, ncol = 1, labels = c("a", "b"))

#ggsave("../../../../results/images/manuscript/S2_MGF_final/S2_MGF_Fig3_v1.png", width = 7, height = 8, units = "in" )

#For manuscript submission
#ggsave("../../../../results/images/manuscript/S2_MGF_final/Fig3_revised.tiff", 
       # width = 200, 
       # height = 200, 
       # units = "mm",
       # dpi = 600)

```


### Get group specific thresholds

How many samples are necessary for confidence intervals to overlap with confidence intervals when all samples are used?  Uses another function written by Jon Lefcheck.

```{r}

#Load multSE function
minsamp <- source_url("https://raw.githubusercontent.com/jslefche/multSE/master/R/minsamp.R")[[1]]

minsamp.fung <- minsamp(out.multiSE.fungi, group = sample_data(voi)$site_season)
minsamp.unfiltered <- minsamp.fung

minsamp.unfiltered$filtered <- "NO"

```

#Same analysis with filtered samples

Filter out rare species to see how if affects results.  Write results of both to table.

```{r}
Sys.time()
voi <- fung.2season_with_outliers_filtered
voi.dm <- distance(voi, method = "bray")
out.multiSE.fungi <- multSE(mat = voi.dm, 
                            group = sample_data(voi)$site_season, 
                            nresamp = 10000, 
                            permanova = FALSE)
Sys.time()

minsamp.fung <- minsamp(out.multiSE.fungi, group = sample_data(voi)$site_season)
minsamp.filtered <- minsamp.fung

minsamp.filtered$filtered <- "YES"

multSE.table <- rbind(minsamp.filtered, minsamp.unfiltered)

#Rename columns to be a little more intuitive
colnames(multSE.table) <- c("Group", "Centroid Mean - Full Set", " Lower CI - Full Set", "Upper CI - Full Set", "Min. number of samples needed")

#write.csv(multSE.table, file = "../../../../results/images/manuscript/S2_MGF_final/S2_MGF_fig3_minsamp_table.csv", row.names = FALSE)

```


### PERMANOVA

Run PERMANOVA on Bray-Curtis dissimilarity, Jaccard index, and Aitchison distance.  Both filtered and unfiltered versions were run depending on which line was uncommented below.  Ran PERMANOVAs with and without oil to corroborate the dbRDA run afterward.

Set up data first.

```{r}

set.seed(1)

voi <- fung.2season_with_outliers
#voi <- fung.2season_with_outliers_filtered

df.full <- voi %>%
  otu_table() %>%
  data.frame() %>%
  t()

df.env <- voi %>%
  sample_data() %>%
  data.frame()

df.env.na <- data.frame(sample_data(voi)) %>%
  select(SampleID,
         site,
         season,
         Total.relevant.PAHs) %>%
  na.omit()

df.full.na<- df.full[rownames(df.full) %in% rownames(df.env.na),]

```

Run PERMANOVA.  Interesting note on [how to choose permutation number](https://www.researchgate.net/post/How_do_I_know_how_many_permutations_to_use). 

#### Bray-Curtis

```{r}

set.seed(1)

adonis(formula = df.full ~ site*season, data = df.env, method = "bray", permutations = 9999)

adonis(formula = df.full.na ~ site*season + Total.relevant.PAHs, data = df.env.na, method = "bray", permutations = 9999)

```

##### Jaccard

```{r}

set.seed(1)

adonis(formula = df.full ~ site*season, data = df.env, method = "jaccard", permutations = 9999, binary = TRUE)

adonis(formula = df.full.na ~ site*season + Total.relevant.PAHs, data = df.env.na, method = "jaccard", permutations = 9999, binary = TRUE)

```

##### Aitchison distance

```{r}

clr.df <- clr(df.full)
clr.df <- as.data.frame(clr.df)

clr.df.na <- clr(df.full.na) %>%
  as.data.frame()

adonis(formula = clr.df ~ site*season, data = df.env, method = "euclidean", permutations = 9999)

adonis(formula = clr.df.na ~ site*season + Total.relevant.PAHs, data = df.env.na, method = "euclidean", permutations = 9999)

```

### PERMDISP

##### Bray-Curtis

```{r}

A <- vegdist(x = df.full, method = "bray")
anova(betadisper(d = A, group = df.env$site))
anova(betadisper(d = A, group = df.env$season))

```

##### Jaccard 

```{r}

A <- vegdist(x = df.full, method = "jaccard", binary = TRUE)
anova(betadisper(d = A, group = df.env$site))
anova(betadisper(d = A, group = df.env$season))

```

##### Aitchison

```{r}

A <- vegdist(x = clr.df, method = "euclidean")
anova(betadisper(d = A, group = df.env$site))
anova(betadisper(d = A, group = df.env$season))

```

### dbRDA with oil

Looked for relationship between total PAHs and the same three composition metrics used in the PERMANOVA.

##### Bray-Curtis

```{r}

fung.dbRDA.BC <- dbrda(formula = df.full.na ~ site*season + Total.relevant.PAHs, data = df.env.na, dist = "bray", permutations = 9999)

anova(fung.dbRDA.BC, by = "terms")
anova(fung.dbRDA.BC, by = "margin")

```

##### Jaccard

```{r}

fung.dbRDA.JC <- dbrda(formula = df.full.na ~ site*season + Total.relevant.PAHs, data = df.env.na, dist = "jaccard", permutations = 9999, binary = TRUE)

anova(fung.dbRDA.JC, by = "margin")
anova(fung.dbRDA.JC, by = "terms")

```

##### Aitchison

```{r}

fung.dbRDA.AT <- dbrda(formula = clr.df.na ~ site*season + Total.relevant.PAHs, data = df.env.na, dist = "euclidean", permutations = 9999)

anova(fung.dbRDA.AT, by = "margin")
anova(fung.dbRDA.AT, by = "terms")

```

