---
title: 'S2_MGF Figure 2: Alpha Diversity'
author: "Stephen Formel"
date: "11/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width = "100%")
```

### S2_MG Manuscript: Figure 2 - alpha diversity

#by Steve Formel

Description:  What does alpha diversity look like? How many samples are necessary to legitimately describe salt marsh soil microbial communities?


_Note that winter = time point 1 and summer = time point 2.  This is leftover from earilier analyses.  I was asked to change these terms in the manuscript revisions, and I didn't have time to completely revise the scripts._


### load libraries

```{r, message = FALSE}

library(cowplot)
library(tidyverse)
library(iNEXT)
library(Rmisc)
library(ggforce)

```

### Color palette

```{r}

cPAL <- c("#E69F00", "#0072B2")

```


### Load and Clean data

```{r, message = FALSE}

source("./S2_MGF_load_packages_and_clean_data.R")
```

### Traditional alpha diversity approach

This is a more traditional approach of estimating alpha diversity.  Abundance weighted diversity is calculated for each sample and then summary statistics are calculated for the site and time point.

```{r}

p <- plot_richness(fung.2season_with_outliers)

#convert value to Hill numbers

p1 <- p$data
p1$value[which(p1$variable == "Observed")] <- p1$value[which(p1$variable == "Observed")]
p1$value[which(p1$variable == "Shannon")] <- exp(p1$value[which(p1$variable == "Shannon")])
p1$value[which(p1$variable == "Simpson")] <- 1/(1 - p1$value[which(p1$variable == "Simpson")])

p1$hill_order <- NA

p1$hill_order[which(p1$variable == "Observed")] <- 0
p1$hill_order[which(p1$variable == "Shannon")] <- 1
p1$hill_order[which(p1$variable == "Simpson")] <- 2

#rename levels for site
p1$site <- as.factor(p1$site)
levels(p1$site) <- plyr:::revalue(levels(p1$site), c("BJ" = "Bay Jimmy", "F" = "Fourchon"))

p1$season <- factor(p1$season, levels = c("WINTER", "SUMMER"))
p1$season <- plyr:::revalue(p1$season, replace = c("WINTER" = "Time Point 1", "SUMMER" = "Time Point 2"))

p1.summary <- summarySE(data = p1,
                        measurevar = "value",
                        groupvars = c("site", "season", "hill_order"))

```

### Plot Traditional alpha diversity

This is figure 2A

```{r}

avg.abund.plot <- p1.summary %>%
  filter(hill_order %in% c(0,2)) %>%
  ggplot(aes(x = site,
           y = value,
           shape = factor(hill_order))) +
  facet_wrap(~ season) +
  geom_errorbar(aes(ymax = value + ci,
                    ymin = value-ci),
                width = 0.2) + 
  geom_point(inherit.aes = FALSE, 
             aes(x = site,
                 y = value),
              shape = 21, 
              fill = "white",
              color = "black",
              size = 3,
             stroke = 0.5) +
  geom_point(size = 2) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  labs(x = "Site",
     y = "Effective Number of Species",
     shape = "Hill Order") +
  scale_shape_manual(values = c(48,50)) +
  guides(shape = guide_legend(label = FALSE, override.aes = list(size = 4))) +
  facet_grid(cols = vars(season),
              rows = vars(hill_order),
              scales = "free") 

```

### Run iNEXT Abundance-weighted estimator

This estimates effective number of species for the entire site.  So, for example, richness is the summed richness of all samples at a given site and time point.  The error is estimated through bootstrapping.

```{r}

#Source script to run iNEXT in parallel

source("./iNEXT_parallel.R")

#melt phyloseq data to data frame
mdf <- psmelt(fung.2season_with_outliers)

# compute taxa sum according to sample type
sampletype_abund <- dplyr::group_by(mdf, OTU, site,season) %>% 
  dplyr::summarise(abundance = sum(Abundance))

df.taxasums <- sampletype_abund %>%
pivot_wider(names_from = c(site,season), names_sep = ".", values_from = c(abundance)) %>%
  as.data.frame() 

df.taxasums1 <- df.taxasums[,-1]
rownames(df.taxasums1) <- df.taxasums[,1]

#not parallel
#Sys.time()
#iNEXT(x = df.taxasums1, 
#                        q = c(0,2),
#                       datatype = "abundance",
#                       se = TRUE,
#                       conf = 0.95,
#                       nboot = 1000,
#                       endpoint = 600000)
# Sys.time()

#10 seconds

Sys.time()
abund.out <- iNEXT_parallel(x = df.taxasums1, 
                       q = c(0,2),
                      datatype = "abundance",
                      multithread = TRUE,
                      se = TRUE,
                      conf = 0.95,
                      nboot = 1000,
                      endpoint = 600000)
Sys.time() 

#under a minute with nboot = 1000, endpoint = 1000
#about 4 minutes with nboot = 1000, endpoint = 10000
#about 27 minutes with nboot = 1000, endpoint = 100000
#about 1-2 hours with nboot = 1000, endpoint = 600000

#If you're pressed for time, q = 1 is the reason this takes so long.  q =0,2 are done in minutes

#Throws a warning that can be ignored.


# Extract results (list with data.frames for each sample)

voi.inext.all.abund <- rbindlist(abund.out)

#add names column
voi.inext.all.abund$group <- rep(names(abund.out), each = 80)
voi.inext.all.abund$site <- c(rep("Heavily Oiled", 160), 
                        rep("Lightly Oiled", 160))

voi.inext.all.abund$season <- rep(c(rep("Summer", 80), rep("Winter", 80)), 2)

#adjust factors
voi.inext.all.abund$season <- factor(voi.inext.all.abund$season, levels = c("Winter", "Summer"))
voi.inext.all.abund$order <- factor(voi.inext.all.abund$order)
```

### Plot of Abundance-weighted diversity 

This is Figure 2B.

```{r}

#Just Hill order =  0 and 2
voi.inext.all.abund <- voi.inext.all.abund %>%
  filter(order %in% c(0,2), method=="observed")

abund.plot <- voi.inext.all.abund %>%
  ggplot(aes(x = site,
           y = qD,
           shape = factor(order))) +
  facet_wrap(~ season) +
  geom_errorbar(aes(ymax = qD.UCL,
                    ymin = qD.LCL),
                width = 0.2) + 
  geom_point(inherit.aes = FALSE, 
             aes(x = site,
                 y = qD),
              shape = 21, 
              fill = "white",
              color = "black",
              size = 3,
             stroke = 0.5) +
  geom_point(size = 2) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  labs(x = "Site",
     y = "Effective Number of Species",
     shape = "Hill Order") +
  scale_shape_manual(values = c(48,50)) +
  guides(shape = guide_legend(label = FALSE, override.aes = list(size = 4))) +
  facet_grid(cols = vars(season),
              rows = vars(order),
              scales = "free") 

```


### Run iNEXT incidence-based estimator

This estimates effective number of species for Hill orders where species are only counted as present/absent and then weighted by presence/absence across all samples.  So, for example, richness = diversity if you only use one sample.  I'm also able to extract curves to show how this diversity builds with samlpe accumulation.  Error is estimated through bootstrapping.

```{r}

voi.list <- list(fung.2season.BJ.summer_with_outliers, 
                 fung.2season.BJ.winter_with_outliers, 
                 fung.2season.F.summer_with_outliers, 
                 fung.2season.F.winter_with_outliers)

#make otu_table_list
voi.list.OT <- lapply(voi.list, function(x) {
  as.data.frame(otu_table(x))
  })

#add names
names(voi.list.OT) <- c("fung.2season.BJ.summer_with_outliers", 
                        "fung.2season.BJ.winter_with_outliers", 
                        "fung.2season.F.summer_with_outliers", 
                        "fung.2season.F.winter_with_outliers")


voi.list.OT <- lapply(voi.list.OT, function(x){
  x[x>0] <- 1
  return(x)  #important to remember this line of code
})


Sys.time()
voi.inext.df.inc <- iNEXT(x = voi.list.OT,
                      q = c(0,2),
                      datatype = "incidence_raw",
                      size = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30),
                      se = TRUE,
                      conf = 0.95,
                      nboot = 1000)
Sys.time()

#took about 30 seconds

#make into one list
voi.inext.all <- rbindlist(voi.inext.df.inc$iNextEst)

#add names column
voi.inext.all$group <- rep(names(voi.inext.df.inc$iNextEst), each = 60)
voi.inext.all$site <- c(rep("Heavily Oiled", 120), 
                        rep("Lightly Oiled", 120))

voi.inext.all$season <- rep(c(rep("Summer", 60), rep("Winter", 60)), 2)

#adjust factors
voi.inext.all$season <- factor(voi.inext.all$season, levels = c("Winter", "Summer"))
voi.inext.all$order <- factor(voi.inext.all$order)

```

### Plot Incidence-base diversity

This is Figure 2C

```{r}

voi.inext.all <- voi.inext.all %>%
  filter(order %in% c(0,2))

inc.plot <- voi.inext.all %>%
  ggplot(aes(x = t,
           y = qD,
           fill = site,
           shape = order)) +
  geom_ribbon(aes(ymax = qD.UCL,
                    ymin = qD.LCL),
               alpha = 0.5) +
  geom_line(inherit.aes = FALSE, data = voi.inext.all %>%
              filter(method=="extrapolated"),
             aes(x = t,
                 y = qD,
                 group = interaction(site, order)),
             color = "black",
             size = 0.5,
            linetype = "dashed")  +
  geom_point(inherit.aes = FALSE, data = voi.inext.all %>%
              filter(method!="extrapolated"), 
             aes(x = t,
                 y = qD,
                 fill = site,
                 shape = order),
           size = 2, fill = "gray") +
  facet_wrap(~ season) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(from = 0, to = 30, by = 5)) +
  labs(x = "Number of Soil Cores",
     y = "Effective Number of Species",
     shape = "Hill Order",
     fill = "Site") +
  theme(legend.text = element_text(size = 10),
        legend.position = "bottom") +
  scale_shape_manual(values = c(48,50)) +
  scale_fill_manual(values = c("black", "darkgray")) +
  guides(shape = guide_legend(label = FALSE, override.aes = list(size = 4)))

```

#Figure 2

```{r}

avg.abundance <- p1.summary
total.abundance <- voi.inext.all.abund %>% 
  select(order, qD, qD.LCL, qD.UCL, group) %>% 
  separate(col = group, into = c("site", "season"), sep = "\\.")

#rename levels for site
total.abundance$site <- as.factor(total.abundance$site)
levels(total.abundance$site) <- plyr:::revalue(levels(total.abundance$site), c("BJ" = "Bay Jimmy", "F" = "Fourchon"))

total.abundance$season <- factor(total.abundance$season, levels = c("WINTER", "SUMMER"))
total.abundance$season <- plyr:::revalue(total.abundance$season, replace = c("WINTER" = "Time Point 1", "SUMMER" = "Time Point 2"))

#get data uniform
avg.abundance$UCI <- avg.abundance$ci + avg.abundance$value
avg.abundance$LCI <- avg.abundance$value - avg.abundance$ci

avg.abundance <- avg.abundance %>% 
  select(hill_order, value, LCI, UCI, site, season)


names(total.abundance) <- c("hill_order", "value", "LCI", "UCI", "site", "season")

#incidence

voi.inext.all$group <- str_remove(voi.inext.all$group, pattern = "fung.2season.")
voi.inext.all$group <- str_remove(voi.inext.all$group, pattern = "_with_outliers")

inc.abundance <- voi.inext.all %>%
  filter(method=="observed") %>% 
  select(order, qD, qD.LCL, qD.UCL, group) %>% 
  separate(col = group, into = c("site", "season"), sep = "\\.")

#rename levels for site
inc.abundance$site <- as.factor(inc.abundance$site)
levels(inc.abundance$site) <- plyr:::revalue(levels(inc.abundance$site), c("BJ" = "Bay Jimmy", "F" = "Fourchon"))

inc.abundance$season <- factor(inc.abundance$season, levels = c("winter", "summer"))
inc.abundance$season <- plyr:::revalue(inc.abundance$season, replace = c("winter" = "Time Point 1", "summer" = "Time Point 2"))

avg.abundance$method <- "Plot-Level"
total.abundance$method <- "Site-Level"
inc.abundance$method <- "Site-Level\nIncidence-Based"

names(inc.abundance) <- c("hill_order", "value", "LCI", "UCI", "site", "season", "method")

#plot
df <- rbind(avg.abundance, total.abundance, inc.abundance)

#make unique values for mean and CI
df <- df %>% 
  pivot_wider(names_from = hill_order, values_from = c(value, UCI, LCI)) 

top <- df %>% 
  ggplot(aes(x = value_2,
             y = value_0,
             color = season,
             shape = site))  +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = LCI_0,
                    ymax = UCI_0),
                size = 0.2) +
  geom_errorbarh(aes(xmin = LCI_2,
                    xmax = UCI_2),
                size = 0.2) +
  geom_mark_rect(aes(group = method,
                     label = method),
                 color = "black",
                 con.type = "straight",
                 expand = 0.05,
                 label.fill = "lightgray",
                 label.buffer = unit(10, 'mm')) +
  theme_bw() +
  scale_color_manual(values = cPAL) +
  #facet_grid(~ method) +
  expand_limits(x = 0, y = 0) +
  xlim(0,175) +
  ylim(0,175) +
  labs(x = "Hill Order = 2",
       y = "Hill Order = 0",
       color = "Time Point",
       shape = "Site")

top
#bottom

#rename levels for site
voi.inext.all$site <- as.factor(voi.inext.all$site)
levels(voi.inext.all$site) <- plyr:::revalue(levels(voi.inext.all$site), c("Heavily Oiled" = "Bay Jimmy", "Lightly Oiled" = "Fourchon"))

voi.inext.all$season <- factor(voi.inext.all$season, levels = c("Winter", "Summer"))

bottom <- voi.inext.all %>%
  ggplot(aes(x = t,
           y = qD,
           fill = season,
           shape = site)) +
  geom_ribbon(aes(ymax = qD.UCL,
                    ymin = qD.LCL),
               alpha = 0.5) +
  geom_line(inherit.aes = FALSE, data = voi.inext.all %>%
              filter(method=="extrapolated"),
             aes(x = t,
                 y = qD,
                 group = interaction(site, season)),
             color = "black",
             size = 0.5,
            linetype = "dashed")  +
  geom_point(inherit.aes = FALSE, data = voi.inext.all %>%
              filter(method!="extrapolated"), 
             aes(x = t,
                 y = qD,
                 fill = season,
                 shape = site),
           size = 2, fill = "gray") +
  facet_grid(~ order,labeller = labeller(order = c("0" = "Hill Order = 0", "2" = "Hill Order = 2"))) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(from = 0, to = 30, by = 5)) +
  labs(x = "Number of Soil Cores",
     y = "Effective Number of Species",
     shape = "Site",
     fill = "Time Point") +
  theme(legend.text = element_text(size = 10),
        legend.position = "bottom") +
  scale_fill_manual(values = cPAL) +
  guides(shape = guide_legend(label = TRUE, override.aes = list(size = 4),
                              order = 2))

bottom
```

## Plot for submission revision

```{r}
# 
# plot_grid(top + theme(legend.position = "none"), 
# bottom + theme(legend.position = "bottom"), 
# labels = c("a", "b"), ncol = 1, nrow = 2)


#For manuscript submission

#ggsave("../../../../results/images/manuscript/S2_MGF_final/Fig2_revised.tiff", 
       # width = 200, 
       # height = 200, 
       # units = "mm",
       # dpi = 600)

#For manuscript submission

# #ggsave("../../../../results/images/manuscript/S2_MGF_final/Fig2_revised.tiff", 
#        width = 200, 
#        height = 200, 
#        units = "mm",
#        dpi = 600)

```

### Calculate min samples needed

For each site and time point, how many samples are needed to be the same, statistically, as when alpha diversity is calculated from all available samples.

```{r}

voi.hill <- subset(voi.inext.all, method=="observed")

#split data frame into list
voi.inext.list <- split.data.frame(voi.inext.all, voi.inext.all$group)

minsamp.list.0 <- list()
#minsamp.list.1 <- list()
minsamp.list.2 <- list()

voi.hill.0 <- subset(voi.hill, order==0)
#voi.hill.1 <- subset(voi.hill, order==1)
voi.hill.2 <- subset(voi.hill, order==2)

for(i in 1:nrow(voi.hill.0)){
  
  minsamp.list.0[[i]] <- voi.inext.list[[voi.hill.0$group[i]]] %>%
    as.data.frame(value = names(voi.inext.list[[voi.hill.0$group[i]]])) %>%
    filter(order==0 & qD.UCL < voi.hill.0[i]$qD.LCL) %>%
    select(t, order, group) %>%
    slice(n())
}
  
# for(i in 1:nrow(voi.hill.0)){
#   
#   minsamp.list.1[[i]] <- voi.inext.list[[voi.hill.1$group[i]]] %>%
#     as.data.frame(value = names(voi.inext.list[[voi.hill.1$group[i]]])) %>%
#     filter(order==1 & qD.UCL < voi.hill.1[i]$qD.LCL) %>%
#     select(t, order, group) %>%
#     slice(n())
# }
 
for(i in 1:nrow(voi.hill.0)){
 minsamp.list.2[[i]] <- voi.inext.list[[voi.hill.2$group[i]]] %>%
    as.data.frame(value = names(voi.inext.list[[voi.hill.2$group[i]]])) %>%
    filter(order==2 & qD.UCL < voi.hill.2[i]$qD.LCL) %>%
    select(t, order, group) %>%
    slice(n())
}

#lists of threshold.  Remember that you need to add one to this because the code above asked to return the samples that had lower CI values
A <- rbindlist(minsamp.list.0)
#B <- rbindlist(minsamp.list.1)
C <- rbindlist(minsamp.list.2)

#make into pretty table
voi.hill.table <- voi.hill %>%
  select(site,season, order,qD,qD.LCL, qD.UCL,t ) %>%
  arrange(order)


voi.hill.table$min.samples <- NA
voi.hill.table$min.samples[voi.hill.table$order==0] <- A$t +1
#voi.hill.table$min.samples[voi.hill.table$order==1] <- B$t + 1
voi.hill.table$min.samples[voi.hill.table$order==2] <- C$t + 1
         
names(voi.hill.table) <- c("Site", "Season", "q (Hill order)", "Effective Number of Species", "Lower CI", "Upper CI","N", "Min. Samples")

voi.hill.table$estimate_type <- "Observed"
voi.hill.table$filtered <- "no"

voi.hill.table.observed.NF <- voi.hill.table

#Extrapolated version

voi.hill <- subset(voi.inext.all, method=="extrapolated") %>%
  filter(t==30)

#split data frame into list
voi.inext.list <- split.data.frame(voi.inext.all, voi.inext.all$group)

minsamp.list.0 <- list()
#minsamp.list.1 <- list()
minsamp.list.2 <- list()

voi.hill.0 <- subset(voi.hill, order==0)
#voi.hill.1 <- subset(voi.hill, order==1)
voi.hill.2 <- subset(voi.hill, order==2)

for(i in 1:nrow(voi.hill.0)){
  
  minsamp.list.0[[i]] <- voi.inext.list[[voi.hill.0$group[i]]] %>%
    as.data.frame(value = names(voi.inext.list[[voi.hill.0$group[i]]])) %>%
    filter(order==0 & qD.UCL < voi.hill.0[i]$qD.LCL) %>%
    select(t, order, group) %>%
    slice(n())
}
  
# for(i in 1:nrow(voi.hill.0)){
#   
#   minsamp.list.1[[i]] <- voi.inext.list[[voi.hill.1$group[i]]] %>%
#     as.data.frame(value = names(voi.inext.list[[voi.hill.1$group[i]]])) %>%
#     filter(order==1 & qD.UCL < voi.hill.1[i]$qD.LCL) %>%
#     select(t, order, group) %>%
#     slice(n())
# }
 
for(i in 1:nrow(voi.hill.0)){
 minsamp.list.2[[i]] <- voi.inext.list[[voi.hill.2$group[i]]] %>%
    as.data.frame(value = names(voi.inext.list[[voi.hill.2$group[i]]])) %>%
    filter(order==2 & qD.UCL < voi.hill.2[i]$qD.LCL) %>%
    select(t, order, group) %>%
    slice(n())
}

#lists of threshold.  Remember that you need to add one to this because the code above asked to return the samples that had lower CI values
A <- rbindlist(minsamp.list.0)
#B <- rbindlist(minsamp.list.1)
C <- rbindlist(minsamp.list.2)

#make into pretty table
voi.hill.table <- voi.hill %>%
  select(site,season, order,qD,qD.LCL, qD.UCL,t ) %>%
  arrange(order)


voi.hill.table$min.samples <- NA
voi.hill.table$min.samples[voi.hill.table$order==0] <- A$t + 1
#voi.hill.table$min.samples[voi.hill.table$order==1] <- B$t + 1
voi.hill.table$min.samples[voi.hill.table$order==2] <- C$t + 1
         
names(voi.hill.table) <- c("Site", "Season", "q (Hill order)", "Effective Number of Species", "Lower CI", "Upper CI","N", "Min. Samples")

voi.hill.table$estimate_type <- "Extrapolated"
voi.hill.table$filtered <- "no"

voi.hill.table.extrapolated.NF <- voi.hill.table

voi.hill.table.extrapolated.NF

```

