---
title: 'S2_MGF: CRMS Salinity'
author: "Stephen Formel"
date: "11/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### S2_MGF Manuscript  Mantel Tests
# by Steve Formel

## Description

No salinity was measured when the soil cores were taken, but I was able to get historical data from a few nearby CRMS sites to illustrate the general sense of how salinity changes at the two site over the year and between the two sites.

_Note that winter = time point 1 and summer = time point 2.  This is leftover from earilier analyses.  I was asked to change these terms in the manuscript revisions, and I didn't have time to completely revise the scripts._

## Load libraries

```{r, message=FALSE}

library(tidyverse)
library(data.table)
library(lubridate)

```

## Import and clean data

```{r}

#data
FL <- list.files(path = "../data/Environmental_data/CRMS_salinity/", pattern = "*0.csv", recursive = TRUE, full.names = TRUE)

df.list <- lapply(FL, read_csv)

df <- rbindlist(df.list)

#spatial info
FL <- list.files(path = "../data/Environmental_data/CRMS_salinity/", pattern = "*1.csv", recursive = TRUE, full.names = TRUE)

df.list <- lapply(FL, read_csv)

df.spatial <- rbindlist(df.list)

#make Station ID a factor

df$Station_ID <- as.factor(df$Station_ID)

```

Make groups of stations that relate to my sites.

```{r}

df$site <- ifelse(df$Station_ID %in% c("CRMS0164-H01", "CRMS0175-H01", "CRMS0178-H01"), "Lightly Oiled", "Heavily Oiled")

```

Coordinate lat/long and salinity.  

```{r}

df.all <- left_join(x = df, y = df.spatial, by = "Station_ID")

```

Extract month and year

```{r}

df.all$MonDate <- as.POSIXct(df.all$MonDate, format = "%m/%d/%Y %I:%M:%S %p")
df.all$Month_Yr <- format(as.Date(df.all$MonDate), "%Y-%m")
df.all$Month <- format(as.Date(df.all$MonDate), "%m")
df.all$Yr <- format(as.Date(df.all$MonDate), "%Y")

```

Do some exploratory plots and stats.

```{r}

df.all %>% 
  ggplot(aes(x = Month,
             y = Salinity,
             color = site)) + 
  geom_boxplot() +
  facet_wrap(~ Yr)

```

Calculate Mean Salinity

```{r}

df.all %>%
  na.omit() %>% 
  group_by(site, Month) %>% 
  summarise(mean = mean(Salinity),
            sd = sd(Salinity))

df.all %>%
  na.omit() %>% 
  group_by(site) %>% 
  summarise(mean = mean(Salinity),
            sd = sd(Salinity))
```

What about mean salinity during Winter and Summer?

```{r}

df.all %>%
  filter(Month %in% c("12", "01", "06", "07")) %>% 
  na.omit() %>% 
  group_by(site, Month) %>% 
  summarise(mean = mean(Salinity),
            sd = sd(Salinity)) 

```

